Evolution of Flare Rates in GKM Stars Younger than 300 Myr

### 2023-11-17 src/tex/ms.tex
bib updates

\begin{deluxetable}{l r r r r r}[!ht]
\tabletypesize{\footnotesize}
\tablecaption{Adopted Ages of each Young Stellar Population and Number of
Stars per Group \label{tab:sample}}
\tablehead{
\colhead{Population} & \colhead{Age [Myr]} & \colhead{N$_\textrm{stars}$} &
\colhead{Ref.}
}
\startdata
AB Doradus  &  133$_{-20}^{+15}$  &  81  & 1 \\
Blanco 1 & 137.1$^{+7.0}_{-33}$ & 301 & 8\\
Carina  &  45  & 91  & 2\\
Carina-Musca & 32 & 22 & 5\\
Chamaeleon  &  5  &  366  & 3 \\
Columba  &  42  &  126  & 2\\
Greater Taurus Subgroup 5 & 8.5 & 56 & 5\\
Greater Taurus Subgroup 8 & 4.5 & 114 & 5\\
Lower Centaurus Crux &  15  & 590  & 4\\
MELANGE-1 & 250$_{-70}^{+50}$ & 22 & 10\\
Octans  &  35$\pm 5$ &   98  & 6 \\
Pisces Eridanis  &  120  &   176  & 7 \\
Pleiades & 127.4$^{+6.3}_{-10}$ & 1304 & 8\\
$\alpha$ Persei  &  79$_{-2.3}^{+1.5}$  &  467  & 8 \\
IC 2602 corona &  52.5$_{-3.7}^{+2.2}$  & 10  & 8 \\
IC 2602 system &  52.5$_{-3.7}^{+2.2}$  & 138  & 8 \\
NGC 2451A & 48.5 & 44 & 5\\
Oh 59 & 162.2 & 50 & 9\\
Platais 9 & 50 & 99 & 11\\
RSG2 & 126 & 87 & 12\\
Theia 301  &  195  &  372  & 9\\
Theia 95  &  30.2  &  191  & 9\\
TW Hydrae  &  10  &  24  & 2\\
Upper Centaurus  Lupus &  16  &  464  & 4 \\
Upper Scorpius  &  10  &  80  & 4 \\
Vela-CG4  &  33.7  &  352  & 5
\enddata
\tablecomments{Age references: (1) \citet{gagne18_abdmg}; (2) \citet{Bell15};
(3) \citet{luhman07}; (4) \citet{pecaut16}; (5) \citet{kerr21};
(6) \citet{murphy15}; (7) \citet{curtis19}; (8) \citet{galindo22};
(9) \citet{kounkel20}; (10) \citet{tofflemeire21}; (11) \citet{tarricq21};
(12) \citet{roser16}; }
\end{deluxetable}

@@

\begin{equation}\label{eqn:fr}
  \mathcal{R} = \frac{1}{t_\textrm{obs}} \left( \sum_{i=1}^{N} p_i \right)
\end{equation}

@@

Additionally, we analyzed the TESS light curves for all of the ULLYSES targets, when
available at 2-minute cadence. We identified a total of \textcolor{red}{n} flares.
This is inconsistent with the overall flare statistics identified in this work, and is
overall unexpected for young stars which are known to be more magnetically active
\citep{ilin20, feinstein20}. This could suggest that there is some bias in the way
the ULLYSES sample was constructed, and that it is unexpected to find any flares in the
FUV data. Alternatively, it could be that the ongoing accretion luminosity results
in a brighter host star, such that the flares we normally would see are drowned
out by the increased baseline luminosity. We do not include this flare in our
overall statistical analysis of TESS flare rates for young stars.

>>>>

\begin{deluxetable}{l r r r r r}[!ht]
\tabletypesize{\footnotesize}
\tablecaption{Adopted Ages of each Young Stellar Population and Number of
Stars per Group \label{tab:sample}}
\tablehead{
\colhead{Population} & \colhead{Age [Myr]} & \colhead{N$_\textrm{stars}$} &
\colhead{Ref.}
}
\startdata
AB Doradus  &  133$_{-20}^{+15}$  &  81  & 1 \\
Blanco 1 & 137.1$^{+7.0}_{-33}$ & 301 & 8\\
Carina  &  45  & 91  & 2\\
Carina-Musca & 32 & 22 & 5\\
Chamaeleon  &  5  &  366  & 3 \\
Columba  &  42  &  126  & 2\\
Greater Taurus Subgroup 5 & 8.5 & 56 & 5\\
Greater Taurus Subgroup 8 & 4.5 & 114 & 5\\
Lower Centaurus Crux &  15  & 590  & 4\\
MELANGE-1 & 250$_{-70}^{+50}$ & 22 & 10\\
Octans  &  35$\pm 5$ &   98  & 6 \\
Pisces Eridanis  &  120  &   176  & 7 \\
Pleiades & 127.4$^{+6.3}_{-10}$ & 1304 & 8\\
$\alpha$ Persei  &  79$_{-2.3}^{+1.5}$  &  467  & 8 \\
IC 2602 corona &  52.5$_{-3.7}^{+2.2}$  & 10  & 8 \\
IC 2602 system &  52.5$_{-3.7}^{+2.2}$  & 138  & 8 \\
NGC 2451A & 48.5 & 44 & 5\\
Oh 59 & 162.2 & 50 & 9\\
Platais 9 & 50 & 99 & 11\\
RSG2 & 126 & 87 & 12\\
Theia 301  &  195  &  372  & 9\\
Theia 95  &  30.2  &  191  & 9\\
TW Hydrae  &  10  &  24  & 2\\
Upper Centaurus  Lupus &  16  &  464  & 4 \\
Upper Scorpius  &  10  &  80  & 4 \\
Vela-CG4  &  33.7  &  352  & 5
\enddata
\tablecomments{Age references: (1) \citet{gagne18_abdmg}; (2) \citet{Bell15};
(3) \citet{luhman07}; (4) \citet{pecaut16}; (5) \citet{kerr21};
(6) \citet{murphy15}; (7) \citet{curtis19}; (8) \citet{galindo22};
(9) \citet{kounkel20}; (10) \citet{tofflemire21}; (11) \citet{tarricq21};
(12) \citet{roser16}; }
\end{deluxetable}

@@

\begin{equation}\label{eq:fr}
  \mathcal{R} = \frac{1}{t_\textrm{obs}} \left( \sum_{i=1}^{N} p_i \right)
\end{equation}

@@

Additionally, we analyzed the TESS light curves for all of the ULLYSES targets, when
available at 2-minute cadence. We identified a total of \textcolor{red}{n} flares.
This is inconsistent with the overall flare statistics identified in this work, and is
overall unexpected for young stars which are known to be more magnetically active
\citep{ilin19, feinstein20}. This could suggest that there is some bias in the way
the ULLYSES sample was constructed, and that it is unexpected to find any flares in the
FUV data. Alternatively, it could be that the ongoing accretion luminosity results
in a brighter host star, such that the flares we normally would see are drowned
out by the increased baseline luminosity. We do not include this flare in our
overall statistical analysis of TESS flare rates for young stars.
